---
title: "Results from fitting to reference p-curves"
author: "Beth Clarke, Felix Schönbrodt, Angelika Stefan"
date: today
execute:
  cache: true
format: 
  html:
    code-fold: true
    embed-resources: true
---

::: {.callout-note title = "Background"}
While building the simulations (before knowing the actual target p-curve by Clarke et al.), to test our fitting procedure, we used three existing empirical p-curves as targets:

1. **Sotola** (*k* = 1,556 significant p-values): Sotola (2023), Meta-Psychology. [doi](https://doi.org/10.15626/MP.2022.3299) → [results](#sec-sotola)
2. **Wetzels** (*k* = 593): Wetzels et al. (2011), Perspectives on Psychological Science. [doi](https://doi.org/10.1177/...) → [results](#sec-wetzels)
3. **Simonsohn** (*k* = 22): Simonsohn et al. (2014), JEP: General, Figure 3B. [data](http://www.p-curve.com/Supplement/full_pdt.xlsx) → [results](#sec-simonsohn)


In this document, we report the results of the best-fitting simulations for each of those empirical p-curves including: i) visualisations of the top 5 best fitting simulations to each empirical p-curves for each world; ii) fit indices for the best simulations in each world for each empirical p-curve; iii) the parameter values for the top 10 best fitting p-curves (across all worlds) for each empirical p-curve.
:::

# Set-up code: Data wrangling and goodness of fit calculations

```{r}
#| message: false
#| warning: false

# Combine simulation results from all conditions into one big dataset
devtools::load_all("../..") # load fit p curve with updated plot_pcurves() function
library(rio)
library(tidyverse)
library(ggplot2)
library(kableExtra)


# reference p-curves
pcurves <- import("reference-pcurves.csv")

# load the multiple DV simulation results:
simres_realistic <- import("../sim-results/sim_realistic.csv")
simres_realistic$condition <- "multDV_realistic"
simres_worst <- import("../sim-results/sim_worst.csv")
simres_worst$condition <- "multDV_worst"
simres_perfect <- import("../sim-results/sim_perfect.csv")
simres_perfect$condition <- "multDV_perfect"
simres_H0 <- import("../sim-results/sim_H0.csv")
simres_H0$condition <- "multDV_H0"

# Delete unnecessary rows for different reporting strategies from simres_perfect      and simres_H0 (these yield identical results as there is only one p-value)
simres_perfect <- simres_perfect |> filter(strategy == 3)
simres_H0 <- simres_H0 |> filter(strategy == 3)

# load the optional stopping simulation results:
simres_optStop_worst <- import("../sim-results/sim_optStop_worst.csv")
simres_optStop_worst$condition <- "optStop_worst"
simres_optStop_realistic <- import("../sim-results/sim_optStop_realistic.csv")
simres_optStop_realistic$condition <- "optStop_realistic"

simres_multDV <- rbind(simres_realistic, simres_worst, simres_perfect, simres_H0)
simres_multDV$binsum <- rowSums(simres_multDV[, paste0("p", 1:5)])
stopifnot(all(simres_multDV$binsum |> round(6) == 1))
simres_multDV$type <- "multDV"

simres_optStop <- rbind(simres_optStop_realistic, simres_optStop_worst)
simres_optStop$binsum <- rowSums(simres_optStop[, paste0("p", 1:5)])
stopifnot(all(simres_optStop$binsum |> round(6) == 1))
simres_optStop$type <- "optStop"

# Combine simulations from both p-hacking strategies (they have different parameter columns)
simres <- bind_rows(simres_multDV, simres_optStop)

```



```{r}
# Compute G-squared fit statistics
simres$fit_sotola_g2 <- g2(
  observed = simplify2array(pcurves[1, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[1], tol=1e-6)

simres$fit_wetzels_g2 <- g2(
  observed = simplify2array(pcurves[2, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[2], tol=1e-6)

simres$fit_simonsohn_g2 <- g2(
  observed = simplify2array(pcurves[3, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[3], tol=1e-6)
```


```{r}
# Also compute chi-squared and RMSE for robustness checks
# Chi-squared
simres$fit_sotola_chi2 <- chi2(
  observed = simplify2array(pcurves[1, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[1], tol=1e-6)

simres$fit_wetzels_chi2 <- chi2(
  observed = simplify2array(pcurves[2, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[2], tol=1e-6)

simres$fit_simonsohn_chi2 <- chi2(
  observed = simplify2array(pcurves[3, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[3], tol=1e-6)

# RMSE
simres$fit_sotola_rmse <- rmse(
  observed = simplify2array(pcurves[1, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[1])

simres$fit_wetzels_rmse <- rmse(
  observed = simplify2array(pcurves[2, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[2])

simres$fit_simonsohn_rmse <- rmse(
  observed = simplify2array(pcurves[3, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[3])
```


```{r}
# Compute BICs for between-world comparisons (accounting for model complexity)

# Number of free parameters in each simulated "world"
simres$free_parameters <- recode_values(simres$condition,
                                     "multDV_realistic" ~ 7,
                                     "multDV_worst" ~ 4,
                                     "multDV_perfect" ~ 3,
                                     "multDV_H0" ~ 0,
                                     "optStop_realistic" ~ 7,
                                     "optStop_worst" ~ 4)

# Compute BIC from G-squared and number of free parameters
simres$BIC_sotola <- simres$fit_sotola_g2 + simres$free_parameters * log(pcurves$nsig[1])

simres$BIC_wetzels <- simres$fit_wetzels_g2 + simres$free_parameters * log(pcurves$nsig[1])

simres$BIC_simonsohn <- simres$fit_simonsohn_g2 + simres$free_parameters * log(pcurves$nsig[1])
```

```{r}
# Save condition labels for later use
condition_labels <- c(
  multDV_perfect    = "Perfect World",
  multDV_H0         = "Flat World",
  multDV_realistic  = "Realistic World: Multiple DVs",
  multDV_worst      = "Worst World: Multiple DVs",
  optStop_realistic = "Realistic World: Optional stopping",
  optStop_worst     = "Worst World: Optional stopping"
)
```


# 1. Target p-curve: Sotola (2023): {#sec-sotola}

## Visualisations of best simulations in each world

You can visually inspect the fit of the top 5 (where available) simulations in each world (in blue) to the target p-curve (in black). Note that the Flat World only involved one simuulation.

::: {.panel-tabset}
## Realistic: Multiples DVs
```{r}
plot_pcurves(simres |> filter(condition == "multDV_realistic"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Multiple DVs")
```
## Realistic: Optional Stopping
```{r}
plot_pcurves(simres |> filter(condition == "optStop_realistic"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Optional Stopping")
```
## Worst: Multiple DVs
```{r}
plot_pcurves(simres |> filter(condition == "multDV_worst"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Worst Possible World: Multiple DVs")
```
## Worst: Optional Stopping
```{r}
plot_pcurves(simres |> filter(condition == "optStop_worst"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Worst Possible World: Optional Stopping")
```
## Perfect
```{r}
plot_pcurves(simres |> filter(condition == "multDV_perfect"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Perfect World")
```
## Flat
```{r}
plot_pcurves(simres |> filter(condition == "multDV_H0"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Flat World")
```
:::

## Overview of best fitting simulations in each world

These fit indices reflect the fit of the best-fitting simulation in each condition/ world. Lower numbers indicate better fit. Note that BIC is a transformation of G2 that penalises for model complexity. 
```{r}
fit_tab <- simres %>%
  group_by(condition) %>%
  summarise(
    G2   = min(fit_sotola_g2),
    BIC  = min(BIC_sotola),
    Chi2 = min(fit_sotola_chi2),
    RMSE = min(fit_sotola_rmse)
  ) 

fit_tab %>%
  mutate(condition = recode(condition, !!!condition_labels)) %>%
  mutate(across(
    -condition,
    ~ cell_spec(sprintf("%.2f", .x), bold = .x == min(.x))
  )) %>%
  kbl(escape = FALSE) %>%
  kable_styling()
```


According to G2, the Realistic World: Optional stopping contained the best-fitting simulation to the target p-curve. Once model complexity is accounted for, the Perfect World contained the simulation with the best fit to the target p-curve. Results for chi-squared and RMSE are also provided as robustness checks.

## What were the top 10 best fitting simulations (according to G^2)?

These rows reflect the 10 simulations that had the best fit to the target p-curve according to G^2. (Scroll to see the other fit indices for these simulations.)

```{r}
simres |> arrange(fit_sotola_g2) |> slice(1:10) |> 
  select(condition, nvar, r, d, prop_Hacker, prop_H1, het, strategy, nmin, nmax, stepsize, contains("sotola")) |>
  kbl(digits = 2) |>
  kable_styling() |>
  scroll_box(width = "100%", height = "400px")
```

# 2. Target p-curve: Wetzels (2011): {#sec-wetzels}

## Visualisations of best simulations in each world

You can visually inspect the fit of the top 5 (where available) simulations in each world (in blue) to the target p-curve (in black). Note that the Flat World only involved one simuulation.

::: {.panel-tabset}

## Realistic: Multiple DVs
```{r}
plot_pcurves(simres |> filter(condition == "multDV_realistic"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Multiple DVs")
```
## Realistic: Optional Stopping
```{r}
plot_pcurves(simres |> filter(condition == "optStop_realistic"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Optional Stopping")
```
## Worst: Multiple DVs
```{r}
plot_pcurves(simres |> filter(condition == "multDV_worst"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Worst Possible World: Multiple DVs")
```
## Worst: Optional Stopping
```{r}
plot_pcurves(simres |> filter(condition == "optStop_worst"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Worst Possible World: Optional Stopping")
```
## Perfect
```{r}
plot_pcurves(simres |> filter(condition == "multDV_perfect"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Perfect World")
```
## Flat
```{r}
plot_pcurves(simres |> filter(condition == "multDV_H0"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Flat World")
```

:::

## Overview of best fitting simulations in each world

These fit indices reflect the fit of the best-fitting simulation in each condition/ world. Lower numbers indicate better fit. Note that BIC is a transformation of G2 that penalises for model complexity.
```{r}
fit_tab <- simres %>%
  group_by(condition) %>%
  summarise(
    G2   = min(fit_wetzels_g2),
    BIC  = min(BIC_wetzels),
    Chi2 = min(fit_wetzels_chi2),
    RMSE = min(fit_wetzels_rmse)
  ) 

fit_tab %>%
  mutate(condition = recode(condition, !!!condition_labels)) %>%
  mutate(across(
    -condition,
    ~ cell_spec(sprintf("%.2f", .x), bold = .x == min(.x))
  )) %>%
  kbl(escape = FALSE) %>%
  kable_styling()
```


According to G2, the Realistic World: Multiple DVs contained the best-fitting simulation to the target p-curve. Once model complexity is accounted for, the Perfect World contained the simulation with the best fit to the target p-curve. Results for chi-squared and RMSE are also provided as robustness checks.

## What were the top 10 best fitting simulations (according to G^2)?

These rows reflect the 10 simulations that had the best fit to the target p-curve according to G^2. (Scroll to see the other fit indices for these simulations.)

```{r}
simres |> arrange(fit_wetzels_g2) |> slice(1:10) |> 
  select(condition, nvar, r, d, prop_Hacker, prop_H1, het, strategy, nmin, nmax, stepsize, contains("wetzels")) |>
  kbl(digits = 2) |>
  kable_styling() |>
  scroll_box(width = "100%", height = "400px")
```

# 3. Target p-curve: Simonsohn (2014): {#sec-simonsohn}

## Visualisations of best simulations in each world

You can visually inspect the fit of the top 5 (where available) simulations in each world (in blue) to the target p-curve (in black). Note that the Flat World only involved one simuulation.

::: {.panel-tabset}
## Realistic: Multiple DVs
```{r}
plot_pcurves(simres |> filter(condition == "multDV_realistic"), poriginal = simplify2array(pcurves[3, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Multiple DVs")
```
## Realistic: Optional Stopping
```{r}
plot_pcurves(simres |> filter(condition == "optStop_realistic"), poriginal = simplify2array(pcurves[3, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Optional Stopping")
```
## Worst: Multiple DVs
```{r}
plot_pcurves(simres |> filter(condition == "multDV_worst"), poriginal = simplify2array(pcurves[3, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Worst Possible World: Multiple DVs")
```
## Worst: Optional Stopping
```{r}
plot_pcurves(simres |> filter(condition == "optStop_worst"), poriginal = simplify2array(pcurves[3, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Worst Possible World: Optional Stopping")
```
## Perfect
```{r}
plot_pcurves(simres |> filter(condition == "multDV_perfect"), poriginal = simplify2array(pcurves[3, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Perfect World")
```
## Flat
```{r}
plot_pcurves(simres |> filter(condition == "multDV_H0"), poriginal = simplify2array(pcurves[3, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Flat World")
```
:::
## Overview of best fitting simulations in each world

These fit indices reflect the fit of the best-fitting simulation in each condition/ world. Lower numbers indicate better fit. Note that BIC is a transformation of G2 that penalises for model complexity.
```{r}
fit_tab <- simres %>%
  group_by(condition) %>%
  summarise(
    G2   = min(fit_simonsohn_g2),
    BIC  = min(BIC_simonsohn),
    Chi2 = min(fit_simonsohn_chi2),
    RMSE = min(fit_simonsohn_rmse)
  ) 

fit_tab %>%
  mutate(condition = recode(condition, !!!condition_labels)) %>%
  mutate(across(
    -condition,
    ~ cell_spec(sprintf("%.2f", .x), bold = .x == min(.x))
  )) %>%
  kbl(escape = FALSE) %>%
  kable_styling()
```


According to G2, the Realistic World: Multiple DVs contained the best-fitting simulation to the target p-curve. Once model complexity is accounted for, the Flat World contained the simulation with the best fit to the target p-curve. Results for chi-squared and RMSE are also provided as robustness checks.

## What were the top 10 best fitting simulations (according to G^2)?

These rows reflect the 10 simulations that had the best fit to the target p-curve according to G^2. (Scroll to see the other fit indices for these simulations.)

```{r}
simres |> arrange(fit_simonsohn_g2) |> slice(1:10) |> 
  select(condition, nvar, r, d, prop_Hacker, prop_H1, het, strategy, nmin, nmax, stepsize, contains("simonsohn")) |>
  kbl(digits = 2) |>
  kable_styling() |>
  scroll_box(width = "100%", height = "400px")
```


