---
title: "plots_for_paper"
author: "Beth Clarke"
output: html_document
date: "2026-03-20"
---
# Setup
```{r setup, include=FALSE}
library(fitPCurve)
library(rio)
library(tidyverse)
library(ggplot2)
library(scales)
library(patchwork)
library(GGally)
library(RColorBrewer)
library(grid)
library(ggnewscale)

# The working directory should be the project root
# if quarto:render is called
if (!interactive()) {
  print("Switching working directory to project root")
  setwd("..")
}

# reference p-curves
pcurves <- import("simulations/avg_pcurve_simulation_study/avg_pcurve.csv")

# p-curves with 500 iterations
pcurves500 <- import("simulations/avg_pcurve_simulation_study/avg_pcurve_500.csv") %>% 
  filter(sample.num != 00) #these are the average p-curves computed above

# load the multiple DV simulation results:
simres <- import("simulations/sim-results/simres_full.RData")

```

### Reshaping
Re-shape pcurves500 into long form
```{r}
pcurves500_long <- pcurves500 %>% 
  pivot_longer(cols = c(p1:p5), names_to = "pval", values_to = "yval")

  pcurves500_long$pval <- substr(pcurves500_long$pval, 2, 2) |> as.numeric()
  pcurves500_long$pval <- pcurves500_long$pval / 100
```

# Figure 1
## Prep
Calculate number of simulations for each p-curve
```{r}
n_sims <- simres %>% 
  group_by(condition) %>% 
  summarise(simulations = n()) #%>% 
  #mutate(simulations = ifelse(condition == "multDV_H0", 1, simulations))

get_n <- function(cond) n_sims$simulations[n_sims$condition == cond]
```


Define p-curving function
```{r}
alpha_ramp <- function(x, min_alpha=0.05, max_alpha=1, min=5, max=1000) {
  a <- max_alpha + (min_alpha-1) * (x - min) / (max - min)
  pmin(max_alpha, pmax(min_alpha, a))
}

#' Plot original and fitted p-curves
#' @description Create a plot displaying the original and a number of fitted p-curves
#' @param simdat Result of simulation function
#' @param poriginal Original p-curve (vector)
#' @param GOF Goodness of fit measure: one of "rmse", "chi2", "g2" (default)
#' @param n_best Show only the n best curves. If NA, all are shown
#' @param alpha Alpha transparency for the simulated p-curve lines
#' @param n_studies Number of studies in the original p-curve (only needed for chi2 GOF)
#' @param tol Numeric tolerance for probability sum checks (default 1e-10).
#' @param ylim Y-axis limits (default c(0, 0.75))
#' @param linewidth_main Linewidth for the empirical and best-fitting simulated lines (default 1.3)
#' @param linewidth_bg Linewidth for the background simulated lines (default 0.4)
#' @import ggplot2
#' @importFrom tidyr pivot_longer
#' @importFrom scales percent
#' @export
plot_pcurves_new <- function(simdat, poriginal, GOF = "g2", n_best = NA, alpha = NA,
                             n_studies = NA, tol = 1e-10, title = "",
                             background_dat = NULL, ylim = c(0, 0.75),
                             linewidth_main = 1.2, linewidth_bg = 0.4,
                             panel_fill = "white") {
  
  stopifnot(all(poriginal >= 0) & all(poriginal <= 1))
  
  # Compute GOF between original and simulated
  if (GOF == "rmse") {
    simdat$GOF <- rmse(observed = poriginal, expected = simdat[, paste0("p", 1:5)])
  } else if (GOF == "chi2") {
    if (is.na(n_studies)) stop("For chi2 GOF, n_studies must be provided")
    simdat$GOF <- chi2(observed = poriginal, expected = simdat[, paste0("p", 1:5)],
                       n = n_studies, tol = tol)
  } else if (GOF == "g2") {
    if (is.na(n_studies)) stop("For G2 GOF, n_studies must be provided")
    simdat$GOF <- g2(observed = poriginal, expected = simdat[, paste0("p", 1:5)],
                     n = n_studies, tol = tol)
  } else {
    stop("GOF must be one of 'rmse', 'chi2', or 'g2'")
  }
  
  simdat$condition <- 1:nrow(simdat)
  
  # Select n_best curves ordered by GOF
  if (is.na(n_best)) n_best <- nrow(simdat)
  
  simdat_sel <- simdat[order(simdat$GOF)[1:n_best], c("condition", paste0("p", 1:5))]
  simdat_sel_long <- pivot_longer(simdat_sel,
                                  cols = matches("p\\d"),
                                  values_to = "yval")
  simdat_sel_long$pval <- substr(simdat_sel_long$name, 2, 2) |> as.numeric()
  simdat_sel_long$pval <- simdat_sel_long$pval / 100
  
  plotdat <- data.frame(pval = seq(0.01, 0.05, by = 0.01),
                        yval = unlist(poriginal))
  
  if (is.na(alpha)) alpha <- alpha_ramp(n_best)
  
  p1 <- ggplot() +
    theme_classic() +
    scale_y_continuous(
      labels = percent,
      limits = ylim
    ) +
    scale_x_continuous(
      breaks = seq(0.01, 0.05, by = 0.01),
      expand = expansion(mult = 0.02)
    ) +
    labs(x = "p-value bin", y = "% of p-values") +
    theme(axis.title = element_text(size = 18),
          axis.text  = element_text(size = 15),
          plot.title = element_text(size = 20),
          panel.background = element_rect(fill = panel_fill, color = NA))
  
  # Background lines first (render behind everything else)
  if (!is.null(background_dat)) {
    p1 <- p1 + geom_line(data = background_dat,
                         aes(y = yval, x = pval, group = sample.num),
                         color = "grey80", alpha = 0.4, linewidth = linewidth_bg)
  }
  
  p1 <- p1 +
    geom_line(data = simdat_sel_long, aes(y = yval, x = pval, group = condition),
              color = "#4287f5", alpha = 0.9, linewidth = linewidth_main) +
    geom_line(data = plotdat, aes(y = yval, x = pval, group = 1),
              linewidth = linewidth_main, alpha = 0.7) +
    ggtitle(title)
  
  p1
}

### Build p-curves
plot_dvr <-  plot_pcurves_new(simres |> filter(condition == "multDV_realistic"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "", background_dat = pcurves500_long |> filter(dataset == "2010-2012"))

plot_optr <- plot_pcurves_new(simres |> filter(condition == "optStop_realistic"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "", background_dat = pcurves500_long |> filter(dataset == "2010-2012"))

plot_dvw <- plot_pcurves_new(simres |> filter(condition == "multDV_worst"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "", background_dat = pcurves500_long |> filter(dataset == "2010-2012"))

plot_optw <- plot_pcurves_new(simres |> filter(condition == "optStop_worst"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "", background_dat = pcurves500_long |> filter(dataset == "2010-2012"))

plot_perf <- plot_pcurves_new(simres |> filter(condition == "multDV_perfect"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "", background_dat = pcurves500_long |> filter(dataset == "2010-2012"))

plot_flat <- plot_pcurves_new(simres |> filter(condition == "multDV_H0"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "", background_dat = pcurves500_long |> filter(dataset == "2010-2012"))


### Function to add circles that indicate n of simulations

add_n_circle <- function(plot, cond, max_n, min_size = 5, max_size = 10) {
  n <- get_n(cond)
  # Rescale log so smallest n maps to min_size and largest to max_size
  size <- min_size + (max_size - min_size) * ((log(n) - log(min(n_sims$simulations))) / 
                                             (log(max_n) - log(min(n_sims$simulations))))^0.5
  
  circle_grob <- grobTree(
    circleGrob(
      x = unit(1, "npc") - unit(size + 2, "mm"),
      y = unit(1, "npc") - unit(size + 2, "mm"),
      r = unit(size, "mm"),
      gp = gpar(fill = "red", col = "red", alpha = 0.15)
    ),
    textGrob(
      label = as.character(n),
      x = unit(1, "npc") - unit(size + 2, "mm"),
      y = unit(1, "npc") - unit(size + 2, "mm"),
      gp = gpar(col = "darkred", fontsize = size * 1.8, fontface = "bold", alpha = 0.6)
    )
  )
  
  plot +
    annotation_custom(grob = circle_grob,
                      xmin = -Inf, xmax = Inf, 
                      ymin = -Inf, ymax = Inf) +
    coord_cartesian(clip = "off")
}

# Add circles to plots
plot_dvr_c  <- add_n_circle(plot_dvr,  "multDV_realistic",  max_n)
plot_dvw_c  <- add_n_circle(plot_dvw,  "multDV_worst",      max_n)
plot_optr_c <- add_n_circle(plot_optr, "optStop_realistic", max_n)
plot_optw_c <- add_n_circle(plot_optw, "optStop_worst",     max_n)
plot_perf_c <- add_n_circle(plot_perf, "multDV_perfect",    max_n)
plot_flat_c <- add_n_circle(plot_flat, "multDV_H0",         max_n)
```


### helpers
```{r}
# ── Helper themes ─────────────────────────────────────────────────────────────
no_y         <- theme(axis.title.y = element_blank(),
                      axis.text.y  = element_blank(),
                      axis.ticks.y = element_blank())
no_title        <- theme(plot.title   = element_blank())
no_x_title      <- theme(axis.title.x = element_blank(),
                          axis.text.x  = element_blank(),
                          axis.ticks.x = element_blank())
no_x_label_only <- theme(axis.title.x = element_blank())
no_y_title      <- theme(axis.title.y = element_blank())
center_title    <- theme(plot.title   = element_text(hjust = 0.5, face = "bold", size = 22))

# ── Label  ──────────────────────
row_label <- function(label) {
  ggplot() +
    annotate("text", x = 0.5, y = 0.5, label = label,
             angle = 90, size = 22/2.835, fontface = "bold") +
    theme_void() +
    theme(plot.margin = margin(0, 0, 0, 0))
}

y_label <- function() {
  ggplot() +
    annotate("text", x = 0.5, y = 0.5, label = "% of p-values",
             angle = 90, size = 18/2.835) +
    theme_void() +
    theme(plot.margin = margin(0, 0, 0, 0))
}

# ── Separator line ────────────────────────────────────────────────────────────
line <- wrap_elements(full = grobTree(
  linesGrob(x = unit(c(0,1), "npc"), y = unit(c(0.5, 0.5), "npc"),
            gp = gpar(lwd = 2.5))
))
```

## F1 option 1
```{r}
# ── Data plots ────────────────────────────────────────────────────────────────
row1_data <- (plot_dvr_c + ggtitle("Realistic World") + center_title + no_x_title + no_y_title |  
              plot_spacer() |
              plot_dvw_c + no_y + ggtitle("Worst World") + center_title + no_x_title) +
  plot_layout(widths = c(1, 0.05, 1))

row2_data <- (plot_optr_c + no_y_title + no_title + no_x_title |
              plot_spacer() |
              plot_optw_c + no_y + no_title + no_x_title) +
  plot_layout(widths = c(1, 0.05, 1))

row3_data <- (plot_perf_c + no_x_label_only + no_y_title |
              plot_spacer() |
              plot_flat_c + no_y + no_x_label_only) +
  plot_layout(widths = c(1, 0.05, 1))

# ── Rows 1 & 2 ─────────────────────
rows_12 <- ((row_label("Multiple DVs") / row_label("Optional Stopping")) |
              y_label() |
              (row1_data / row2_data)) +
  plot_layout(widths = c(0.08, 0.086, 1))


# ── Row 3 ──────────────────────────────────────────
row3_data <- (plot_perf_c + ggtitle("Perfect World") + center_title + no_x_label_only + no_y_title |
              plot_spacer() |
              plot_flat_c + ggtitle("Flat World") + center_title + no_y + no_x_label_only) +
  plot_layout(widths = c(1, 0.05, 1)) +
  plot_annotation(
    title = "Other Worlds",
    theme = theme(
      plot.title = element_text(hjust = 0.5, face = "bold", size = 22), 
      plot.margin = margin(t = 5, b = 0, l = 0, r = 0)
    )
  )

row3_with_title <- wrap_elements(full = patchworkGrob(row3_data))

row_3 <- (row_label("") | 
           y_label() |
           row3_with_title) +
  plot_layout(widths = c(0.08, 0.06, 1))

# ── Shared x-axis label (offset matches label col width) ─────────────────────
x_label_row <- (plot_spacer() |
  plot_spacer() |
  ggplot() +
  annotate("text", x = 0.5, y = 0.5, label = "p-value bin", size = 18/2.835) +
  theme_void() +
  theme(plot.margin = margin(0, 0, 0, 0))) +
  plot_layout(widths = c(0.08, 0.06, 1))

# ── Assemble ──────────────────────────────────────────────────────────────────
rows_12 / line / row_3 / x_label_row +
  plot_layout(heights = c(2, 0.04, 1.25, 0.08)) 

ggsave("p-curve_1/figure1_option1.png", width = 12, height = 12, units = "in")
```

## F1 option 2
```{r figure1-transposed}

# ── Transposed layout: rows = worlds, cols = strategies ───────────────────────

row_realistic <- (plot_dvr_c + ggtitle("Multiple DVs") + center_title + no_x_title + no_y_title |
                  plot_spacer() |
                  plot_optr_c + ggtitle("Optional Stopping") + center_title + no_x_title + no_y) +
  plot_layout(widths = c(1, 0.05, 1))

row_worst <- (plot_dvw_c + no_title + no_x_title + no_y_title |
              plot_spacer() |
              plot_optw_c + no_title + no_x_title + no_y) +
  plot_layout(widths = c(1, 0.05, 1))

row_perfect <- (row_label("Perfect World") + theme(plot.margin = margin(0,0,0,0)) |
                plot_perf_c + no_title + no_x_title + no_y_title |
                plot_spacer()) +
  plot_layout(widths = c(0.5, 1, 0.5))

row_flat <- (row_label("Flat World") + theme(plot.margin = margin(0,0,0,0)) |
             plot_flat_c + no_title + no_x_label_only + no_y_title |
             plot_spacer()) +
  plot_layout(widths = c(0.5, 1, 0.5))

row_labels_transposed <- (row_label("Realistic World") /
                           row_label("Worst World") /
                           plot_spacer() /
                           plot_spacer())

fig1_transposed <- (row_labels_transposed | y_label() | 
                    (row_realistic / row_worst / row_perfect / row_flat)) +
  plot_layout(widths = c(0.12, 0.06, 1))

fig1_transposed / x_label_row +
  plot_layout(heights = c(1, 0.05))

ggsave("p-curve_1/figure1_option2.png", width = 12, height = 14, units = "in")
```

## F1 option 3
```{r}
# Compute BIC for p-curve 1
simres$BIC_p1 <- simres$fit_pcurve1_g2 + simres$free_parameters * log(pcurves$nsig[1])

# Helper to extract best-fit stats for a condition
get_best_stats_p1 <- function(cond) {
  best <- simres |> 
    filter(condition == cond) |> 
    slice_min(fit_pcurve1_g2, n = 1, with_ties = FALSE)
  list(
    g2  = round(best$fit_pcurve1_g2, 2),
    bic = round(best$BIC_p1, 2)
  )
}

# Helper to add stats annotation to a plot
add_stats_p1 <- function(plot, cond) {
  s <- get_best_stats_p1(cond)
  plot + annotate("text", 
                  x = Inf, y = Inf,
                  label = paste0("G² = ", s$g2, "\nBIC = ", s$bic),
                  hjust = 1.1, vjust = 3.5,
                  size = 4, color = "#525252", fontface = "italic")
}

# ── Rows ──────────────────────────────────────────────────────────────────────
row_realistic_p1 <- (add_stats_p1(plot_dvr_c, "multDV_realistic") + 
                       ggtitle("Multiple DVs") + center_title + no_x_title + no_y_title |
                     plot_spacer() |
                     add_stats_p1(plot_optr_c, "optStop_realistic") + 
                       ggtitle("Optional Stopping") + center_title + no_x_title + no_y) +
  plot_layout(widths = c(1, 0.05, 1))

row_worst_p1 <- (add_stats_p1(plot_dvw_c, "multDV_worst") + 
                   no_title + no_x_title + no_y_title |
                 plot_spacer() |
                 add_stats_p1(plot_optw_c, "optStop_worst") + 
                   no_title + no_x_title + no_y) +
  plot_layout(widths = c(1, 0.05, 1))

row_perfect_p1 <- (row_label("Perfect World") + theme(plot.margin = margin(0,0,0,0)) |
                   add_stats_p1(plot_perf_c, "multDV_perfect") + 
                     no_title + no_x_title + no_y_title |
                   plot_spacer()) +
  plot_layout(widths = c(0.5, 1, 0.5))

row_flat_p1 <- (row_label("Flat World") + theme(plot.margin = margin(0,0,0,0)) |
                add_stats_p1(plot_flat_c, "multDV_H0") + 
                  no_title + no_x_label_only + no_y_title |
                plot_spacer()) +
  plot_layout(widths = c(0.5, 1, 0.5))

# ── Assemble ──────────────────────────────────────────────────────────────────
row_labels_transposed_p1 <- (row_label("Realistic World") /
                              row_label("Worst World") /
                              plot_spacer() /
                              plot_spacer())

fig1_transposed_p1 <- (row_labels_transposed_p1 | y_label() |
                       (row_realistic_p1 / row_worst_p1 / row_perfect_p1 / row_flat_p1)) +
  plot_layout(widths = c(0.12, 0.06, 1))

fig1_transposed_p1 / x_label_row +
  plot_layout(heights = c(1, 0.05)) 

ggsave("p-curve_1/figure1_option3.png", width = 12, height = 14, units = "in")
```
### option 3 with different themes
```{r}
row_perfect_p1 <- (wrap_elements(row_label("Perfect World") + theme(plot.margin = margin(0,0,0,0))) |
                   add_stats_p1(plot_perf_c, "multDV_perfect") + 
                     no_title + no_x_title + no_y_title |
                   plot_spacer()) +
  plot_layout(widths = c(0.5, 1, 0.5))

row_flat_p1 <- (wrap_elements(row_label("Flat World") + theme(plot.margin = margin(0,0,0,0))) |
                add_stats_p1(plot_flat_c, "multDV_H0") + 
                  no_title + no_x_label_only + no_y_title |
                plot_spacer()) +
  plot_layout(widths = c(0.5, 1, 0.5))

row_labels_transposed_p1_wrapped <- wrap_elements(
  row_label("Realistic World") /
  row_label("Worst World") /
  plot_spacer() /
  plot_spacer()
)

fig1_transposed_p1_minimal <- (row_labels_transposed_p1_wrapped | y_label_wrapped |
                       (row_realistic_p1 / row_worst_p1 / row_perfect_p1 / row_flat_p1)) +
  plot_layout(widths = c(0.12, 0.06, 1)) &
  theme_minimal() &
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 22))

fig1_transposed_p1_bw <- (row_labels_transposed_p1_wrapped | y_label_wrapped |
                       (row_realistic_p1 / row_worst_p1 / row_perfect_p1 / row_flat_p1)) +
  plot_layout(widths = c(0.12, 0.06, 1)) &
  theme_bw() &
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 22))

fig1_transposed_p1_light <- (row_labels_transposed_p1_wrapped | y_label_wrapped |
                       (row_realistic_p1 / row_worst_p1 / row_perfect_p1 / row_flat_p1)) +
  plot_layout(widths = c(0.12, 0.06, 1)) &
  theme_light() &
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 22))

fig1_transposed_p1_minimal / x_label_row +
  plot_layout(heights = c(1, 0.05))
ggsave("p-curve_1/figure1_option3_minimal.png", width = 12, height = 14, units = "in")

fig1_transposed_p1_bw / x_label_row +
  plot_layout(heights = c(1, 0.05))
ggsave("p-curve_1/figure1_option3_bw.png", width = 12, height = 14, units = "in")

fig1_transposed_p1_light / x_label_row +
  plot_layout(heights = c(1, 0.05))
ggsave("p-curve_1/figure1_option3_light.png", width = 12, height = 14, units = "in")
```

# Figure 2
## Prep
### Heat map plotting function
```{r }
plot_heatmap <- function(condition_name, n_top = 100, show_legend = FALSE) {
  
  if (grepl("multDV", condition_name)) {
    vars <- c("prop_Hacker", "prop_H1", "het", "d", "nvar", "r", "strategy")
    labels <- c("Proportion p-hackers", "Proportion true effects", 
                "Heterogeneity (SD of d)", "Effect size (d)", 
                "N variables", "Correlation (r)", "Strategy")
  } else if (grepl("optStop", condition_name)) {
    vars <- c("prop_Hacker", "prop_H1", "het", "d", "nmin", "nmax", "stepsize")
    labels <- c("Proportion p-hackers", "Proportion true effects",
                "Heterogeneity (SD of d)", "Effect size (d)",
                "Min. N.", "Max N.", "Step size N.")
  }
  
  level_lookup_local <- simres |>
    filter(condition == condition_name) |>
    pivot_longer(cols = all_of(vars), names_to = "variable", values_to = "value") |>
    filter(!is.na(value)) |>
    group_by(variable) |>
    summarise(levels = list(sort(unique(value))), .groups = "drop")
  
  var_numeric_local <- setNames(seq_along(vars), vars)
  
  background_dat_local <- level_lookup_local |>
    mutate(y = unname(var_numeric_local[variable])) |>
    rowwise() |>
    mutate(value_norm = list(seq_along(levels)),
           label = list(as.character(levels))) |>
    unnest(c(value_norm, label))
  
  top_n <- simres |>
    filter(condition == condition_name) |>
    slice_min(fit_pcurve1_g2, n = n_top, with_ties = FALSE)
  
  prop_dat <- top_n |>
    pivot_longer(cols = all_of(vars), names_to = "variable", values_to = "value") |>
    filter(!is.na(value)) |>
    left_join(level_lookup_local, by = "variable") |>
    mutate(value_norm = map2_int(value, levels, ~ match(.x, .y)),
           y = unname(var_numeric_local[variable])) |>
    group_by(variable, y, value_norm) |>
    summarise(prop = n() / n_top, .groups = "drop")
  
  heatmap_dat <- background_dat_local |>
    left_join(prop_dat, by = c("variable", "y", "value_norm")) |>
    mutate(prop = replace_na(prop, 0),
           text_color = ifelse(prop > 0.5, "white", "grey30"))
  
  p <- heatmap_dat |>
    ggplot(aes(x = value_norm, y = y, fill = prop)) +
    geom_tile(data = background_dat_local,
              aes(x = value_norm, y = y, fill = NULL),
              fill = "white", color = "grey70", width = 1, height = 0.9) +
    geom_tile(aes(width = 1, height = 0.9), alpha = 0.9) +
    geom_text(data = background_dat_local,
              aes(x = value_norm, y = y, label = label, fill = NULL),
              size = 4, fontface = "bold", color = "grey30") +
    geom_text(data = heatmap_dat,
              aes(x = value_norm, y = y, label = label, color = text_color, fill = NULL),
              size = 4, fontface = "bold") +
    scale_color_identity() +
    scale_fill_gradient(low = "white", high = "#fe9929",
                        name = "Proportion\nin top 100",
                        labels = scales::percent,
                        limits = c(0, 1),
                        oob = scales::squish) +
    scale_y_continuous(breaks = seq_along(vars), labels = vars) +
    theme_minimal() +
    theme(panel.grid = element_blank(),
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          legend.position = if (show_legend) "right" else "none")
  
  list(plot = p, heatmap_dat = heatmap_dat)
}
```

## F2 option 1 - Marginal heatmap
```{r}
hm_dvr  <- plot_heatmap("multDV_realistic")$plot
hm_dvw  <- plot_heatmap("multDV_worst")$plot
hm_optr <- plot_heatmap("optStop_realistic")$plot
hm_optw <- plot_heatmap("optStop_worst", show_legend = TRUE)$plot

# Plot labeling
# ── Row label helper (reuse existing row_label function) ──────────────────────
hm_row1 <- (plot_spacer() |
             hm_dvr + no_y_title |
             plot_spacer() |
             hm_dvw + no_y) +
  plot_layout(widths = c(0.001, 1, 0.05, 1))

hm_row2 <- (plot_spacer() |
             hm_optr + no_y_title |
             plot_spacer() |
             hm_optw + no_y) +
  plot_layout(widths = c(0.001, 1, 0.05, 1))

hm_rows_12 <- ((row_label("Multiple DVs") / row_label("Optional Stopping")) |
                (hm_row1 / hm_row2)) +
  plot_layout(widths = c(0.06, 1))

col_title_row <- (plot_spacer() | col_titles) +
  plot_layout(widths = c(0.06, 1))

col_title_row / hm_rows_12 +
  plot_layout(heights = c(0.05, 1))

ggsave("p-curve_1/figure2_option1.png", width = 12, height = 10, units = "in")
```


## F2 option 2 - Profile coordinates plot
```{r}
# For the paper, we will only show the profile plot for the world with the simulation that has the highest g^2.

top_condition <- simres$condition[which.min(simres$fit_pcurve1_g2)] # which condition had the simulation with the highest g^2

level_lookup <- simres |> # create a reference point of the variables and their values (note: some of these variables only apply to the optional stopping condition, the multiDV variables are not included here)
  pivot_longer(cols = c(prop_Hacker, prop_H1, het, d, nmin, nmax, stepsize),
               names_to = "variable", values_to = "value") |>
  group_by(variable) |>
  summarise(levels = list(sort(unique(value))), .groups = "drop") 

# Set the order
var_levels <- c("prop_Hacker", "prop_H1", "het", "d", "nmin", "nmax",  "stepsize")
var_numeric <- setNames(seq_along(var_levels), var_levels)

# Recode to readable labels
var_levels <- recode(var_levels,
  "prop_Hacker" = "Proportion p-hackers",
  "prop_H1"     = "Proportion true effects",
  "het"         = "Heterogeneity (SD of d)",
  "d"           = "Effect size (d)",
  "nmin"        = "Min. N.",
  "nmax"        = "Max N.",
  "stepsize"    = "Step size N."
)

# Prepare the data for plotting
plotdat <- simres |>
  filter(condition == top_condition) |>
  slice_min(fit_pcurve1_g2, n = 5) |>
  pivot_longer(cols = c(d, prop_Hacker, prop_H1, het, nmin, nmax, stepsize),
               names_to = "variable", values_to = "value") |>
  filter(!is.na(value)) |>
  left_join(level_lookup, by = "variable") |>
  mutate(value_norm = map2_int(value, levels, ~ match(.x, .y)), 
         y = var_numeric[variable] ) |>   # numeric y position
  group_by(sim_ID) |>
  mutate(jitter = runif(1, -0.2, 0.2),
         value_norm_j = value_norm + jitter) |>
  ungroup() |>
  arrange(sim_ID, y)  |>
  mutate(sim_ID = reorder(as.factor(sim_ID), fit_pcurve1_g2))

# Create the data frame for the background of the profile plot
background_dat <- level_lookup |>
  filter(!variable %in% c("nvar", "r")) |>
  mutate(y = var_numeric[variable] ) |>
  rowwise() |>
  mutate(value_norm = list(seq_along(levels)),
         label = list(as.character(levels))) |>
  unnest(c(value_norm, label))
```

```{r }
# Plot!
profile_plot_p1 <- plotdat |>
  ggplot(aes(x = value_norm_j, y = y, group = sim_ID, color = fit_pcurve1_g2)) +
  geom_tile(data = background_dat,
            aes(x = value_norm, y = y, group = NULL),
            fill = "white", color = "grey70", width = 1, height = 0.9) +
  geom_path(alpha = 1, size = 2) +
  geom_point(alpha = 1, size = 2) +
  geom_label(data = background_dat,
           aes(x = value_norm, y = y, label = label, group = NULL),
           size = 4, color = "grey20", fill = alpha("white", 0.5),
           label.size = 0,
           label.padding = unit(0.1, "lines")) +
  scale_color_gradient(high = "#d7e3f5", low = "#4287f5",
                       name = "Simulation fit (G²)",
                       guide = guide_colorbar(reverse = TRUE)) +
  scale_y_continuous(breaks = seq_along(var_levels), labels = var_levels) +
  theme_minimal(base_size = 14) +
  theme(panel.grid = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(
    title = "Top 5 Best-Fitting Simulations for P-Curve 1 in the 
'Optional Stopping Realistic' World",
    x = "Parameter Value",
    y = "Parameter"
  )


# Figure 2 -- best fitting p-curve world with profile plot
(plot_optr + profile_plot_p1)

ggsave("p-curve_1/figure2_option2.png", width = 12, height = 5, units = "in")
```

## F2 option 3 - combined
```{r}
hm_top_out  <- plot_heatmap(top_condition, show_legend = TRUE)
hm_top      <- hm_top_out$plot
heatmap_dat <- hm_top_out$heatmap_dat

hm_with_profile <- hm_top +
  ggnewscale::new_scale_color() +
  geom_path(data = plotdat,
            aes(x = value_norm_j, y = y, group = sim_ID, color = fit_pcurve1_g2),
            linewidth = 3, alpha = 0.7,
            inherit.aes = FALSE) +
  geom_point(data = plotdat,
             aes(x = value_norm_j, y = y, color = fit_pcurve1_g2),
             size = 3, alpha = 1,
             inherit.aes = FALSE) +
  scale_color_gradient(high = "#d7e3f5", low = "#4287f5",
                       name = "Simulation fit (G²)",
                       guide = guide_colorbar(reverse = TRUE)) +
  scale_y_continuous(breaks = seq_along(var_levels), labels = var_levels) +
  ggnewscale::new_scale_color() +
  geom_text(data = heatmap_dat,
            aes(x = value_norm, y = y, label = label, color = text_color),
            size = 4, fontface = "bold",
            inherit.aes = FALSE) +
  scale_color_identity()

plot_optr | (hm_with_profile + no_y_title)
ggsave("p-curve_1/figure2_option3.png", width = 14, height = 6, units = "in")
```
# P-curve 2
## Figure 1 option 1
```{r}
### Build p-curves
plot_dvr_p2 <-  plot_pcurves_new(simres |> filter(condition == "multDV_realistic"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Multiple DVs", background_dat = pcurves500_long |> filter(dataset == "2016-2019"))

plot_optr_p2 <- plot_pcurves_new(simres |> filter(condition == "optStop_realistic"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Optional Stopping", background_dat = pcurves500_long |> filter(dataset == "2016-2019"))

plot_dvw_p2 <- plot_pcurves_new(simres |> filter(condition == "multDV_worst"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "", background_dat = pcurves500_long |> filter(dataset == "2016-2019"))

plot_optw_p2 <- plot_pcurves_new(simres |> filter(condition == "optStop_worst"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "", background_dat = pcurves500_long |> filter(dataset == "2016-2019"))

plot_perf_p2 <- plot_pcurves_new(simres |> filter(condition == "multDV_perfect"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "", background_dat = pcurves500_long |> filter(dataset == "2016-2019"))

plot_flat_p2 <- plot_pcurves_new(simres |> filter(condition == "multDV_H0"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "", background_dat = pcurves500_long |> filter(dataset == "2016-2019"))


# Add circles to plots
plot_dvr_c_p2  <- add_n_circle(plot_dvr_p2,  "multDV_realistic",  max_n)
plot_dvw_c_p2  <- add_n_circle(plot_dvw_p2,  "multDV_worst",      max_n)
plot_optr_c_p2 <- add_n_circle(plot_optr_p2, "optStop_realistic", max_n)
plot_optw_c_p2 <- add_n_circle(plot_optw_p2, "optStop_worst",     max_n)
plot_perf_c_p2 <- add_n_circle(plot_perf_p2, "multDV_perfect",    max_n)
plot_flat_c_p2 <- add_n_circle(plot_flat_p2, "multDV_H0",         max_n)
```


## F1 option 1
```{r}
# ── Data plots ────────────────────────────────────────────────────────────────
row1_data_p2 <- (plot_dvr_c_p2 + ggtitle("Realistic World") + center_title + no_x_title + no_y_title |  
              plot_spacer() |
              plot_dvw_c_p2 + no_y + ggtitle("Worst World") + center_title + no_x_title) +
  plot_layout(widths = c(1, 0.05, 1))

row2_data_p2 <- (plot_optr_c_p2 + no_y_title + no_title + no_x_title |
              plot_spacer() |
              plot_optw_c_p2 + no_y + no_title + no_x_title) +
  plot_layout(widths = c(1, 0.05, 1))

row3_data_p2 <- (plot_perf_c_p2 + no_x_label_only + no_y_title |
              plot_spacer() |
              plot_flat_c_p2 + no_y + no_x_label_only) +
  plot_layout(widths = c(1, 0.05, 1))

# ── Rows 1 & 2 ─────────────────────
rows_12_p2 <- ((row_label("Multiple DVs") / row_label("Optional Stopping")) |
              y_label() |
              (row1_data_p2 / row2_data_p2)) +
  plot_layout(widths = c(0.08, 0.086, 1))

# ── Row 3 ──────────────────────────────────────────
row3_data_p2 <- (plot_perf_c_p2 + ggtitle("Perfect World") + center_title + no_x_label_only + no_y_title |
              plot_spacer() |
              plot_flat_c_p2 + ggtitle("Flat World") + center_title + no_y + no_x_label_only) +
  plot_layout(widths = c(1, 0.05, 1)) +
  plot_annotation(
    title = "Other Worlds",
    theme = theme(
      plot.title = element_text(hjust = 0.5, face = "bold", size = 22), 
      plot.margin = margin(t = 5, b = 0, l = 0, r = 0)
    )
  )

row3_with_title_p2 <- wrap_elements(full = patchworkGrob(row3_data_p2))

row_3_p2 <- (row_label("") | 
           y_label() |
           row3_with_title_p2) +
  plot_layout(widths = c(0.08, 0.06, 1))

# ── Shared x-axis label ─────────────────────────────────────────────────────
x_label_row_p2 <- (plot_spacer() |
  plot_spacer() |
  ggplot() +
  annotate("text", x = 0.5, y = 0.5, label = "p-value bin", size = 18/2.835) +
  theme_void() +
  theme(plot.margin = margin(0, 0, 0, 0))) +
  plot_layout(widths = c(0.08, 0.06, 1))

# ── Assemble ──────────────────────────────────────────────────────────────────
rows_12_p2 / line / row_3_p2 / x_label_row_p2 +
  plot_layout(heights = c(2, 0.04, 1.25, 0.08)) 

ggsave("p-curve_2/figure1_option1.png", width = 12, height = 12, units = "in")
```
## F1 option 2
```{r figure1-transposed}
# ── Transposed layout: rows = worlds, cols = strategies ───────────────────────
row_realistic_p2 <- (plot_dvr_c_p2 + ggtitle("Multiple DVs") + center_title + no_x_title + no_y_title |
                     plot_spacer() |
                     plot_optr_c_p2 + ggtitle("Optional Stopping") + center_title + no_x_title + no_y) +
  plot_layout(widths = c(1, 0.05, 1))

row_worst_p2 <- (plot_dvw_c_p2 + no_title + no_x_title + no_y_title |
                 plot_spacer() |
                 plot_optw_c_p2 + no_title + no_x_title + no_y) +
  plot_layout(widths = c(1, 0.05, 1))

row_perfect_p2 <- (row_label("Perfect World") + theme(plot.margin = margin(0,0,0,0)) |
                   plot_perf_c_p2 + no_title + no_x_title + no_y_title |
                   plot_spacer()) +
  plot_layout(widths = c(0.5, 1, 0.5))

row_flat_p2 <- (row_label("Flat World") + theme(plot.margin = margin(0,0,0,0)) |
                plot_flat_c_p2 + no_title + no_x_label_only + no_y_title |
                plot_spacer()) +
  plot_layout(widths = c(0.5, 1, 0.5))

row_labels_transposed_p2 <- (row_label("Realistic World") /
                              row_label("Worst World") /
                              plot_spacer() /
                              plot_spacer())

fig1_transposed_p2 <- (row_labels_transposed_p2 | y_label() |
                       (row_realistic_p2 / row_worst_p2 / row_perfect_p2 / row_flat_p2)) +
  plot_layout(widths = c(0.12, 0.06, 1))

fig1_transposed_p2 / x_label_row +
  plot_layout(heights = c(1, 0.05))

ggsave("p-curve_2/figure1_option2.png", width = 12, height = 14, units = "in")
```

## F1 option 3 (including G^2 and BIC)
```{r }
# Compute BIC for p-curve 2
simres$BIC_p2 <- simres$fit_pcurve2_g2 + simres$free_parameters * log(pcurves$nsig[2])

# Helper to extract best-fit stats for a condition
get_best_stats_p2 <- function(cond) {
  best <- simres |> 
    filter(condition == cond) |> 
    slice_min(fit_pcurve2_g2, n = 1, with_ties = FALSE)
  list(
    g2  = round(best$fit_pcurve2_g2, 2),
    bic = round(best$BIC_p2, 2)
  )
}

# Helper to add stats annotation to a plot
add_stats_p2 <- function(plot, cond) {
  s <- get_best_stats_p2(cond)
  plot + annotate("text", 
                  x = Inf, y = Inf,
                  label = paste0("G² = ", s$g2, "\nBIC = ", s$bic),
                  hjust = 1.1, vjust = 3.6,
                  size = 4, color = "#525252", fontface = "italic")
}

row_realistic_p2 <- (add_stats_p2(plot_dvr_c_p2, "multDV_realistic") + 
                       ggtitle("Multiple DVs") + center_title + no_x_title + no_y_title |
                     plot_spacer() |
                     add_stats_p2(plot_optr_c_p2, "optStop_realistic") + 
                       ggtitle("Optional Stopping") + center_title + no_x_title + no_y) +
  plot_layout(widths = c(1, 0.05, 1))

row_worst_p2 <- (add_stats_p2(plot_dvw_c_p2, "multDV_worst") + 
                   no_title + no_x_title + no_y_title |
                 plot_spacer() |
                 add_stats_p2(plot_optw_c_p2, "optStop_worst") + 
                   no_title + no_x_title + no_y) +
  plot_layout(widths = c(1, 0.05, 1))

row_perfect_p2 <- (row_label("Perfect World") + theme(plot.margin = margin(0,0,0,0)) |
                   add_stats_p2(plot_perf_c_p2, "multDV_perfect") + 
                     no_title + no_x_title + no_y_title |
                   plot_spacer()) +
  plot_layout(widths = c(0.5, 1, 0.5))

row_flat_p2 <- (row_label("Flat World") + theme(plot.margin = margin(0,0,0,0)) |
                add_stats_p2(plot_flat_c_p2, "multDV_H0") + 
                  no_title + no_x_label_only + no_y_title |
                plot_spacer()) +
  plot_layout(widths = c(0.5, 1, 0.5))

row_labels_transposed_p2 <- (row_label("Realistic World") /
                              row_label("Worst World") /
                              plot_spacer() /
                              plot_spacer())

fig1_transposed_p2 <- (row_labels_transposed_p2 | y_label() |
                       (row_realistic_p2 / row_worst_p2 / row_perfect_p2 / row_flat_p2)) +
  plot_layout(widths = c(0.12, 0.06, 1))

fig1_transposed_p2 / x_label_row +
  plot_layout(heights = c(1, 0.05))

ggsave("p-curve_2/figure1_option3.png", width = 12, height = 14, units = "in")
```

### option 3 with different themes
```{r}
row_perfect_p2 <- (wrap_elements(row_label("Perfect World") + theme(plot.margin = margin(0,0,0,0))) |
                   add_stats_p2(plot_perf_c_p2, "multDV_perfect") + 
                     no_title + no_x_title + no_y_title |
                   plot_spacer()) +
  plot_layout(widths = c(0.5, 1, 0.5))

row_flat_p2 <- (wrap_elements(row_label("Flat World") + theme(plot.margin = margin(0,0,0,0))) |
                add_stats_p2(plot_flat_c_p2, "multDV_H0") + 
                  no_title + no_x_label_only + no_y_title |
                plot_spacer()) +
  plot_layout(widths = c(0.5, 1, 0.5))

row_labels_transposed_p2_wrapped <- wrap_elements(
  row_label("Realistic World") /
  row_label("Worst World") /
  plot_spacer() /
  plot_spacer()
)

fig1_transposed_p2_minimal <- (row_labels_transposed_p2_wrapped | y_label_wrapped |
                       (row_realistic_p2 / row_worst_p2 / row_perfect_p2 / row_flat_p2)) +
  plot_layout(widths = c(0.12, 0.06, 1)) &
  theme_minimal() &
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 22))

fig1_transposed_p2_bw <- (row_labels_transposed_p2_wrapped | y_label_wrapped |
                       (row_realistic_p2 / row_worst_p2 / row_perfect_p2 / row_flat_p2)) +
  plot_layout(widths = c(0.12, 0.06, 1)) &
  theme_bw() &
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 22))

fig1_transposed_p2_light <- (row_labels_transposed_p2_wrapped | y_label_wrapped |
                       (row_realistic_p2 / row_worst_p2 / row_perfect_p2 / row_flat_p2)) +
  plot_layout(widths = c(0.12, 0.06, 1)) &
  theme_light() &
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 22))

fig1_transposed_p2_minimal / x_label_row +
  plot_layout(heights = c(1, 0.05))
ggsave("p-curve_2/figure1_option3_minimal.png", width = 12, height = 14, units = "in")

fig1_transposed_p2_bw / x_label_row +
  plot_layout(heights = c(1, 0.05))
ggsave("p-curve_2/figure1_option3_bw.png", width = 12, height = 14, units = "in")

fig1_transposed_p2_light / x_label_row +
  plot_layout(heights = c(1, 0.05))
ggsave("p-curve_2/figure1_option3_light.png", width = 12, height = 14, units = "in")
```

## Figure 2

## F2 option 1 - Marginal heatmap
```{r }
hm_dvr_p2  <- plot_heatmap("multDV_realistic")$plot
hm_dvw_p2  <- plot_heatmap("multDV_worst")$plot
hm_optr_p2 <- plot_heatmap("optStop_realistic")$plot
hm_optw_p2 <- plot_heatmap("optStop_worst", show_legend = TRUE)$plot

hm_row1_p2 <- (plot_spacer() |
               hm_dvr_p2 + no_y_title |
               plot_spacer() |
               hm_dvw_p2 + no_y) +
  plot_layout(widths = c(0.001, 1, 0.05, 1))

hm_row2_p2 <- (plot_spacer() |
               hm_optr_p2 + no_y_title |
               plot_spacer() |
               hm_optw_p2 + no_y) +
  plot_layout(widths = c(0.001, 1, 0.05, 1))

hm_rows_12_p2 <- ((row_label("Multiple DVs") / row_label("Optional Stopping")) |
                   (hm_row1_p2 / hm_row2_p2)) +
  plot_layout(widths = c(0.06, 1))

col_title_row / hm_rows_12_p2 +
  plot_layout(heights = c(0.05, 1))

ggsave("p-curve_2/figure2_option1.png", width = 12, height = 10, units = "in")
```

## F2 option 2 - Profile coordinates plot
```{r}
top_condition_p2 <- simres$condition[which.min(simres$fit_pcurve2_g2)]

level_lookup_p2 <- simres |>
  filter(condition == top_condition_p2) |>
  pivot_longer(cols = c(prop_Hacker, prop_H1, het, d, nvar, r, strategy),
               names_to = "variable", values_to = "value") |>
  filter(!is.na(value)) |>
  group_by(variable) |>
  summarise(levels = list(sort(unique(value))), .groups = "drop")

var_levels_p2 <- c("prop_Hacker", "prop_H1", "het", "d", "nvar", "r", "strategy")
var_numeric_p2 <- setNames(seq_along(var_levels_p2), var_levels_p2)

var_levels_p2 <- recode(var_levels_p2,
  "prop_Hacker" = "Proportion p-hackers",
  "prop_H1"     = "Proportion true effects",
  "het"         = "Heterogeneity (SD of d)",
  "d"           = "Effect size (d)",
  "nvar"        = "N variables",
  "r"           = "Correlation (r)",
  "strategy"    = "Strategy"
)

plotdat_p2 <- simres |>
  filter(condition == top_condition_p2) |>
  slice_min(fit_pcurve2_g2, n = 5) |>
  pivot_longer(cols = c(prop_Hacker, prop_H1, het, d, nvar, r, strategy),
               names_to = "variable", values_to = "value") |>
  filter(!is.na(value)) |>
  left_join(level_lookup_p2, by = "variable") |>
  mutate(value_norm = map2_int(value, levels, ~ match(.x, .y)),
         y = var_numeric_p2[variable]) |>
  group_by(sim_ID) |>
  mutate(jitter = runif(1, -0.2, 0.2),
         value_norm_j = value_norm + jitter) |>
  ungroup() |>
  arrange(sim_ID, y) |>
  mutate(sim_ID = reorder(as.factor(sim_ID), fit_pcurve2_g2))

background_dat_p2 <- level_lookup_p2 |>
  mutate(y = var_numeric_p2[variable]) |>
  rowwise() |>
  mutate(value_norm = list(seq_along(levels)),
         label = list(as.character(levels))) |>
  unnest(c(value_norm, label))
```

```{r}
profile_plot_p2 <- plotdat_p2 |>
  ggplot(aes(x = value_norm_j, y = y, group = sim_ID, color = fit_pcurve2_g2)) +
  geom_tile(data = background_dat_p2,
            aes(x = value_norm, y = y, group = NULL),
            fill = "white", color = "grey70", width = 1, height = 0.9) +
  geom_path(alpha = 1, size = 2) +
  geom_point(alpha = 1, size = 2) +
  geom_label(data = background_dat_p2,
             aes(x = value_norm, y = y, label = label, group = NULL),
             size = 4, color = "grey20", fill = alpha("white", 0.5),
             label.size = 0,
             label.padding = unit(0.1, "lines")) +
  scale_color_gradient(high = "#d7e3f5", low = "#4287f5",
                       name = "Simulation fit (G²)",
                       guide = guide_colorbar(reverse = TRUE)) +
  scale_y_continuous(breaks = seq_along(var_levels_p2), labels = var_levels_p2) +
  theme_minimal(base_size = 14) +
  theme(panel.grid = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(
    title = paste0("Top 5 Best-Fitting Simulations for P-Curve 2 in the '",
                   top_condition_p2, "' World"),
    x = "Parameter Value",
    y = "Parameter"
  )

plot_dvr_c_p2 + profile_plot_p2
ggsave("p-curve_2/figure2_option2.png", width = 12, height = 5, units = "in")
```

## F2 option 3 - combined
```{r}
hm_top_out_p2  <- plot_heatmap(top_condition_p2, show_legend = TRUE)
hm_top_p2      <- hm_top_out_p2$plot
heatmap_dat_p2 <- hm_top_out_p2$heatmap_dat

hm_with_profile_p2 <- hm_top_p2 +
  ggnewscale::new_scale_color() +
  geom_path(data = plotdat_p2,
            aes(x = value_norm_j, y = y, group = sim_ID, color = fit_pcurve2_g2),
            linewidth = 3, alpha = 0.7,
            inherit.aes = FALSE) +
  geom_point(data = plotdat_p2,
             aes(x = value_norm_j, y = y, color = fit_pcurve2_g2),
             size = 3, alpha = 1,
             inherit.aes = FALSE) +
  scale_color_gradient(high = "#d7e3f5", low = "#4287f5",
                       name = "Simulation fit (G²)",
                       guide = guide_colorbar(reverse = TRUE)) +
  scale_y_continuous(breaks = seq_along(var_levels_p2), labels = var_levels_p2) +
  ggnewscale::new_scale_color() +
  geom_text(data = heatmap_dat_p2,
            aes(x = value_norm, y = y, label = label, color = text_color),
            size = 4, fontface = "bold",
            inherit.aes = FALSE) +
  scale_color_identity()

plot_dvr_c_p2 | (hm_with_profile_p2 + no_y_title)
ggsave("p-curve_2/figure2_option3.png", width = 14, height = 6, units = "in")
```
