---
title: "Evaluation of p-curve simulation results"
author: "Felix Schönbrodt & Angelika Stefan"
date: today
execute:
  cache: true
format: 
  html:
    code-fold: true
    embed-resources: true
---

## Data wrangling and Goodness of Fit calculation

Combine simulation results from all conditions into one big dataset

```{r}
#| include: false


library(fitPCurve)
library(rio)
library(dplyr)
library(ggplot2)

# The working directory should be the project root
# if quarto:render is called
if (!interactive()) {
  print("Switching working directory to project root")
  setwd("..")
}

# reference p-curves (THIS WILL BE EXCHANGED WITH P-CURVES FROM CLARKE ET AL.)
pcurves <- import("simulations/reference-pcurves.csv")

# load the multiple DV simulation results:
simres_realistic <- import("simulations/sim-results/sim_realistic.csv")
simres_realistic$condition <- "multDV_realistic"
simres_worst <- import("simulations/sim-results/sim_worst.csv")
simres_worst$condition <- "multDV_worst"
simres_perfect <- import("simulations/sim-results/sim_perfect.csv")
simres_perfect$condition <- "multDV_perfect"
simres_H0 <- import("simulations/sim-results/sim_H0.csv")
simres_H0$condition <- "multDV_H0"

# load the optional stopping simulation results:
simres_optStop_worst <- import("simulations/sim-results/sim_optStop_worst.csv")
simres_optStop_worst$condition <- "optStop_worst"
simres_optStop_realistic <- import("simulations/sim-results/sim_optStop_realistic.csv")
simres_optStop_realistic$condition <- "optStop_realistic"

simres_multDV <- rbind(simres_realistic, simres_worst, simres_perfect, simres_H0)
simres_multDV$binsum <- rowSums(simres_multDV[, paste0("p", 1:5)])
stopifnot(all(simres_multDV$binsum |> round(6) == 1))
simres_multDV$type <- "multDV"

simres_optStop <- rbind(simres_optStop_realistic, simres_optStop_worst)
simres_optStop$binsum <- rowSums(simres_optStop[, paste0("p", 1:5)])
stopifnot(all(simres_optStop$binsum |> round(6) == 1))
simres_optStop$type <- "optStop"

# Combine simulations from both p-hacking strategies (they have different parameter columns)
simres <- bind_rows(simres_multDV, simres_optStop)

save(simres, file="simulations/sim-results/simres_all.RData")
save(simres, file="simulations/ShinyApp/simres_all.RData")
```

Compute G-squared fit statistics

```{r}
simres$fit_pcurve1_g2 <- g2(
  observed = simplify2array(pcurves[1, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[1], tol=1e-6)

simres$fit_pcurve2_g2 <- g2(
  observed = simplify2array(pcurves[2, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[2], tol=1e-6)
```

Also compute chi-squared and RMSE for robustness checks

```{r}
# Chi-squared
simres$fit_pcurve1_chi2 <- chi2(
  observed = simplify2array(pcurves[1, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[1], tol=1e-6)
simres$fit_pcurve2_chi2 <- chi2(
  observed = simplify2array(pcurves[2, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[2], tol=1e-6)

# RMSE
simres$fit_pcurve1_rmse <- rmse(
  observed = simplify2array(pcurves[1, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[1])
simres$fit_pcurve2_rmse <- rmse(
  observed = simplify2array(pcurves[2, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[2])
```

## Extract best fits in each "world"

### For the first p-curve:

Extract best fits in each world using G-squared statistic

```{r}
# Worst case, multiple DVs
simres |> filter(condition == "multDV_worst") |> arrange(fit_pcurve1_g2) |> slice(1:5) |> select(c(1:9, 10:14), fit_pcurve1_g2) |> round(2) |> print()
```

```{r}
# Worst case, optional stopping
simres |> filter(condition == "optStop_worst") |> arrange(fit_pcurve1_g2) |> slice(1:5) |> select(c(1:9, 10:14), fit_pcurve1_g2) |> round(2) |> print()
```

```{r}
# Realistic, multiple DVs
simres |> filter(condition == "multDV_realistic") |> arrange(fit_pcurve1_g2) |> slice(1:5) |> select(c(1:9, 10:14), fit_pcurve1_g2) |> round(2) |> print()
```

```{r}
# Realistic, optional stopping
simres |> filter(condition == "optStop_realistic") |> arrange(fit_pcurve1_g2) |> slice(1:5) |> select(c(1:9, 10:14), fit_pcurve1_g2) |> round(2) |> print()
```

```{r}
# Perfect
simres |> filter(condition == "multDV_perfect") |> arrange(fit_pcurve1_g2) |> slice(1:5) |> select(c(1:9, 10:14), fit_pcurve1_g2) |> round(2) |> print()
```

Robustness checks: Check if results change depending on the Goodness of fit statistic

```{r}
simres$sim_ID <- rownames(simres)

# Worst case, multiple DVs
G2_fits <- simres |> filter(condition == "multDV_perfect") |> arrange(fit_pcurve1_g2) |> slice(1:5) |> select("sim_ID", "fit_pcurve1_g2")
Chi2_fits <- simres |> filter(condition == "multDV_perfect") |> arrange(fit_pcurve1_chi2) |> slice(1:5) |> select("sim_ID", "fit_pcurve1_chi2")
RMSE_fits <- simres |> filter(condition == "multDV_perfect") |> arrange(fit_pcurve1_rmse) |> slice(1:5) |> select("sim_ID", "fit_pcurve1_rmse")

worstcase_multDV_fits <- cbind(G2_fits, Chi2_fits, RMSE_fits)
colnames(worstcase_multDV_fits) <- c("G2_best_sims", "G2", "Chi2_best_sims", "Chi2", "RMSE_best_sims", "RMSE")

worstcase_multDV_fits
```

```{r}
# Worst case, optional stopping
G2_fits <- simres |> filter(condition == "optStop_worst") |> arrange(fit_pcurve1_g2) |> slice(1:5) |> select("sim_ID", "fit_pcurve1_g2")
Chi2_fits <- simres |> filter(condition == "optStop_worst") |> arrange(fit_pcurve1_chi2) |> slice(1:5) |> select("sim_ID", "fit_pcurve1_chi2")
RMSE_fits <- simres |> filter(condition == "optStop_worst") |> arrange(fit_pcurve1_rmse) |> slice(1:5) |> select("sim_ID", "fit_pcurve1_rmse")

worstcase_optstop_fits <- cbind(G2_fits, Chi2_fits, RMSE_fits)
colnames(worstcase_optstop_fits) <- c("G2_best_sims", "G2", "Chi2_best_sims", "Chi2", "RMSE_best_sims", "RMSE")

worstcase_optstop_fits
```

```{r}
# Realistic, multiple DVs
G2_fits <- simres |> filter(condition == "multDV_realistic") |> arrange(fit_pcurve1_g2) |> slice(1:5) |> select("sim_ID", "fit_pcurve1_g2")
Chi2_fits <- simres |> filter(condition == "multDV_realistic") |> arrange(fit_pcurve1_chi2) |> slice(1:5) |> select("sim_ID", "fit_pcurve1_chi2")
RMSE_fits <- simres |> filter(condition == "multDV_realistic") |> arrange(fit_pcurve1_rmse) |> slice(1:5) |> select("sim_ID", "fit_pcurve1_rmse")

multDV_realistic_fits <- cbind(G2_fits, Chi2_fits, RMSE_fits)
colnames(multDV_realistic_fits) <- c("G2_best_sims", "G2", "Chi2_best_sims", "Chi2", "RMSE_best_sims", "RMSE")

multDV_realistic_fits
```

```{r}
# Realistic, optional stopping
G2_fits <- simres |> filter(condition == "optStop_realistic") |> arrange(fit_pcurve1_g2) |> slice(1:5) |> select("sim_ID", "fit_pcurve1_g2")
Chi2_fits <- simres |> filter(condition == "optStop_realistic") |> arrange(fit_pcurve1_chi2) |> slice(1:5) |> select("sim_ID", "fit_pcurve1_chi2")
RMSE_fits <- simres |> filter(condition == "optStop_realistic") |> arrange(fit_pcurve1_rmse) |> slice(1:5) |> select("sim_ID", "fit_pcurve1_rmse")

optstop_realistic_fits <- cbind(G2_fits, Chi2_fits, RMSE_fits)
colnames(optstop_realistic_fits) <- c("G2_best_sims", "G2", "Chi2_best_sims", "Chi2", "RMSE_best_sims", "RMSE")

optstop_realistic_fits
```

```{r}
# Perfect
G2_fits <- simres |> filter(condition == "multDV_perfect") |> arrange(fit_pcurve1_g2) |> slice(1:5) |> select("sim_ID", "fit_pcurve1_g2")
Chi2_fits <- simres |> filter(condition == "multDV_perfect") |> arrange(fit_pcurve1_chi2) |> slice(1:5) |> select("sim_ID", "fit_pcurve1_chi2")
RMSE_fits <- simres |> filter(condition == "multDV_perfect") |> arrange(fit_pcurve1_rmse) |> slice(1:5) |> select("sim_ID", "fit_pcurve1_rmse")

perfect_fits <- cbind(G2_fits, Chi2_fits, RMSE_fits)
colnames(perfect_fits) <- c("G2_best_sims", "G2", "Chi2_best_sims", "Chi2", "RMSE_best_sims", "RMSE")

perfect_fits
```
Compute BICs for between-world comparisons (accounting for model complexity)

```{r}
# Number of free parameters in each simulated "world"
simres$free_parameters <- case_match(simres$condition,
                                     "multDV_realistic" ~ 6,
                                     "multDV_worst" ~ 3,
                                     "multDV_perfect" ~ 3,
                                     "multDV_H0" ~ 0,
                                     "optStop_realistic" ~ 7,
                                     "optStop_worst" ~ 4)

# Compute BIC from G-squared and number of free parameters
simres$BIC <- simres$fit_pcurve1_g2 + simres$free_parameters * log(pcurves$nsig[1])

# Compare BICs for best fits
simres |> group_by(condition) |> arrange(fit_pcurve1_g2) |> slice(1) |> select(BIC, fit_pcurve1_g2) |> ungroup() |> print()

```

Visualisation

```{r}
plot_pcurves(simres |> filter(condition == "multDV_realistic"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Multiple DVs")

plot_pcurves(simres |> filter(condition == "optStop_realistic"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Optional Stopping")

plot_pcurves(simres |> filter(condition == "multDV_worst"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Worst Possible World: Multiple DVs")

plot_pcurves(simres |> filter(condition == "optStop_worst"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Worst Possible World: Optional Stopping")

plot_pcurves(simres |> filter(condition == "multDV_perfect"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Perfect World")

plot_pcurves(simres |> filter(condition == "multDV_H0"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Flat World")
```

