---
title: "Results from fitting to reference p-curves"
author: "Beth Clarke, Felix Schönbrodt, Angelika Stefan"
date: today
execute:
  cache: true
format: 
  html:
    code-fold: true
    embed-resources: true
---

# Data wrangling and Goodness of Fit calculation

Combine simulation results from all conditions into one big dataset

```{r}

library(fitPCurve)
library(rio)
library(dplyr)
library(ggplot2)
library(kableExtra)


# reference p-curves
pcurves <- import("reference-pcurves.csv")

# load the multiple DV simulation results:
simres_realistic <- import("sim-results/sim_realistic.csv")
simres_realistic$condition <- "multDV_realistic"
simres_worst <- import("sim-results/sim_worst.csv")
simres_worst$condition <- "multDV_worst"
simres_perfect <- import("sim-results/sim_perfect.csv")
simres_perfect$condition <- "multDV_perfect"
simres_H0 <- import("sim-results/sim_H0.csv")
simres_H0$condition <- "multDV_H0"

# Delete unnecessary rows for different reporting strategies from simres_perfect      and simres_H0 (these yield identical results as there is only one p-value)
simres_perfect <- simres_perfect |> filter(strategy == 3)
simres_H0 <- simres_H0 |> filter(strategy == 3)

# load the optional stopping simulation results:
simres_optStop_worst <- import("sim-results/sim_optStop_worst.csv")
simres_optStop_worst$condition <- "optStop_worst"
simres_optStop_realistic <- import("sim-results/sim_optStop_realistic.csv")
simres_optStop_realistic$condition <- "optStop_realistic"

simres_multDV <- rbind(simres_realistic, simres_worst, simres_perfect, simres_H0)
simres_multDV$binsum <- rowSums(simres_multDV[, paste0("p", 1:5)])
stopifnot(all(simres_multDV$binsum |> round(6) == 1))
simres_multDV$type <- "multDV"

simres_optStop <- rbind(simres_optStop_realistic, simres_optStop_worst)
simres_optStop$binsum <- rowSums(simres_optStop[, paste0("p", 1:5)])
stopifnot(all(simres_optStop$binsum |> round(6) == 1))
simres_optStop$type <- "optStop"

# Combine simulations from both p-hacking strategies (they have different parameter columns)
simres <- bind_rows(simres_multDV, simres_optStop)

```

Compute G-squared fit statistics

```{r}
simres$fit_sotola_g2 <- g2(
  observed = simplify2array(pcurves[1, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[1], tol=1e-6)

simres$fit_wetzels_g2 <- g2(
  observed = simplify2array(pcurves[2, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[2], tol=1e-6)

simres$fit_simonsohn_g2 <- g2(
  observed = simplify2array(pcurves[3, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[3], tol=1e-6)
```

Also compute chi-squared and RMSE for robustness checks

```{r}
# Chi-squared
simres$fit_sotola_chi2 <- chi2(
  observed = simplify2array(pcurves[1, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[1], tol=1e-6)

simres$fit_wetzels_chi2 <- chi2(
  observed = simplify2array(pcurves[2, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[2], tol=1e-6)

simres$fit_simonsohn_chi2 <- chi2(
  observed = simplify2array(pcurves[3, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[3], tol=1e-6)

# RMSE
simres$fit_sotola_rmse <- rmse(
  observed = simplify2array(pcurves[1, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[1])

simres$fit_wetzels_rmse <- rmse(
  observed = simplify2array(pcurves[2, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[2])

simres$fit_simonsohn_rmse <- rmse(
  observed = simplify2array(pcurves[3, paste0("p", 1:5)]), 
  expected = simres[, paste0("p", 1:5)], n = pcurves$nsig[3])
```

Compute BICs for between-world comparisons (accounting for model complexity)

```{r}
# Number of free parameters in each simulated "world"
simres$free_parameters <- case_match(simres$condition,
                                     "multDV_realistic" ~ 6,
                                     "multDV_worst" ~ 3,
                                     "multDV_perfect" ~ 3,
                                     "multDV_H0" ~ 0,
                                     "optStop_realistic" ~ 7,
                                     "optStop_worst" ~ 4)

# Compute BIC from G-squared and number of free parameters
simres$BIC_sotola <- simres$fit_sotola_g2 + simres$free_parameters * log(pcurves$nsig[1])

simres$BIC_wetzels <- simres$fit_wetzels_g2 + simres$free_parameters * log(pcurves$nsig[1])

simres$BIC_simonsohn <- simres$fit_simonsohn_g2 + simres$free_parameters * log(pcurves$nsig[1])
```

```{r}
# Save condition labels for later use
condition_labels <- c(
  multDV_perfect    = "Perfect World",
  multDV_H0         = "Flat World",
  multDV_realistic  = "Realistic World: Multiple DVs",
  multDV_worst      = "Worst World: Multiple DVs",
  optStop_realistic = "Realistic World: Optional stopping",
  optStop_worst     = "Worst World: Optional stopping"
)
```


# Target p-curve: Sotola (2023):

## Visualisations of best simulations in each world

You can visually inspect the fit of the top 5 (where available) simulations in each world (in blue) to the target p-curve (in black).

```{r}
plot_pcurves(simres |> filter(condition == "multDV_realistic"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Multiple DVs")

plot_pcurves(simres |> filter(condition == "optStop_realistic"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Optional Stopping")

plot_pcurves(simres |> filter(condition == "multDV_worst"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Worst Possible World: Multiple DVs")

plot_pcurves(simres |> filter(condition == "optStop_worst"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Worst Possible World: Optional Stopping")

plot_pcurves(simres |> filter(condition == "multDV_perfect"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Perfect World")

plot_pcurves(simres |> filter(condition == "multDV_H0"), poriginal = simplify2array(pcurves[1, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Flat World")
```

## Overview of best fitting simulations in each world

These fit indices reflect the fit of the best-fitting simulation in each condition/ world. Lower numbers indicate better fit. Note that BIC is a transformation of G2 that penalises for model complexity.
```{r}
fit_tab <- simres %>%
  group_by(condition) %>%
  summarise(
    G2   = min(fit_sotola_g2),
    BIC  = min(BIC_sotola),
    Chi2 = min(fit_sotola_chi2),
    RMSE = min(fit_sotola_rmse)
  ) 

fit_tab %>%
  mutate(condition = recode(condition, !!!condition_labels)) %>%
  mutate(across(
    -condition,
    ~ cell_spec(sprintf("%.2f", .x), bold = .x == min(.x))
  )) %>%
  kbl(escape = FALSE) %>%
  kable_styling()
```


According to G2, the Realistic World: Optional stopping contained the best-fitting simulation to the target p-curve. Once model complexity is accounted for, the Perfect World contained the simulation with the best fit to the target p-curve. Results for chi-squared and RMSE are also provided as robustness checks.

## What were the top 10 best fitting simulations (according to G^2)?

These rows reflect the 10 simulations that had the best fit to the target p-curve according to G^2.

```{r}
simres |> arrange(fit_sotola_g2) |> slice(1:10) |> print()
```

# Target p-curve: Wetzels (2011):

## Visualisations of best simulations in each world

You can visually inspect the fit of the top 5 (where available) simulations in each world (in blue) to the target p-curve (in black).

```{r}
plot_pcurves(simres |> filter(condition == "multDV_realistic"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Multiple DVs")

plot_pcurves(simres |> filter(condition == "optStop_realistic"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Optional Stopping")

plot_pcurves(simres |> filter(condition == "multDV_worst"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Worst Possible World: Multiple DVs")

plot_pcurves(simres |> filter(condition == "optStop_worst"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Worst Possible World: Optional Stopping")

plot_pcurves(simres |> filter(condition == "multDV_perfect"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Perfect World")

plot_pcurves(simres |> filter(condition == "multDV_H0"), poriginal = simplify2array(pcurves[2, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Flat World")
```

## Overview of best fitting simulations in each world

These fit indices reflect the fit of the best-fitting simulation in each condition/ world. Lower numbers indicate better fit. Note that BIC is a transformation of G2 that penalises for model complexity.
```{r}
fit_tab <- simres %>%
  group_by(condition) %>%
  summarise(
    G2   = min(fit_wetzels_g2),
    BIC  = min(BIC_wetzels),
    Chi2 = min(fit_wetzels_chi2),
    RMSE = min(fit_wetzels_rmse)
  ) 

fit_tab %>%
  mutate(condition = recode(condition, !!!condition_labels)) %>%
  mutate(across(
    -condition,
    ~ cell_spec(sprintf("%.2f", .x), bold = .x == min(.x))
  )) %>%
  kbl(escape = FALSE) %>%
  kable_styling()
```


According to G2, the Realistic World: Multiple DVs contained the best-fitting simulation to the target p-curve. Once model complexity is accounted for, the Perfect World contained the simulation with the best fit to the target p-curve. Results for chi-squared and RMSE are also provided as robustness checks.

## What were the top 10 best fitting simulations (according to G^2)?

These rows reflect the 10 simulations that had the best fit to the target p-curve according to G^2.

```{r}
simres |> arrange(fit_wetzels_g2) |> slice(1:10) |> print()
```

# Target p-curve: Simonsohn (2014):

## Visualisations of best simulations in each world

You can visually inspect the fit of the top 5 (where available) simulations in each world (in blue) to the target p-curve (in black).

```{r}
plot_pcurves(simres |> filter(condition == "multDV_realistic"), poriginal = simplify2array(pcurves[3, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Multiple DVs")

plot_pcurves(simres |> filter(condition == "optStop_realistic"), poriginal = simplify2array(pcurves[3, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Realistic World: Optional Stopping")

plot_pcurves(simres |> filter(condition == "multDV_worst"), poriginal = simplify2array(pcurves[3, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Worst Possible World: Multiple DVs")

plot_pcurves(simres |> filter(condition == "optStop_worst"), poriginal = simplify2array(pcurves[3, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Worst Possible World: Optional Stopping")

plot_pcurves(simres |> filter(condition == "multDV_perfect"), poriginal = simplify2array(pcurves[3, paste0("p", 1:5)]), n_best = 5, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Perfect World")

plot_pcurves(simres |> filter(condition == "multDV_H0"), poriginal = simplify2array(pcurves[3, paste0("p", 1:5)]), n_best = 1, GOF="g2", n_studies = pcurves$nsig[1], tol = 1e-6, title = "Flat World")
```

## Overview of best fitting simulations in each world

These fit indices reflect the fit of the best-fitting simulation in each condition/ world. Lower numbers indicate better fit. Note that BIC is a transformation of G2 that penalises for model complexity.
```{r}
fit_tab <- simres %>%
  group_by(condition) %>%
  summarise(
    G2   = min(fit_simonsohn_g2),
    BIC  = min(BIC_simonsohn),
    Chi2 = min(fit_simonsohn_chi2),
    RMSE = min(fit_simonsohn_rmse)
  ) 

fit_tab %>%
  mutate(condition = recode(condition, !!!condition_labels)) %>%
  mutate(across(
    -condition,
    ~ cell_spec(sprintf("%.2f", .x), bold = .x == min(.x))
  )) %>%
  kbl(escape = FALSE) %>%
  kable_styling()
```


According to G2, the Realistic World: Multiple DVs contained the best-fitting simulation to the target p-curve. Once model complexity is accounted for, the Flat World contained the simulation with the best fit to the target p-curve. Results for chi-squared and RMSE are also provided as robustness checks.

## What were the top 10 best fitting simulations (according to G^2)?

These rows reflect the 10 simulations that had the best fit to the target p-curve according to G^2.

```{r}
simres |> arrange(fit_simonsohn_g2) |> slice(1:10) |> print()
```


